Analysis of Climate Sensitivity using HadAM3

### 2014-04-27 article.tex
Add a discussion.

The HadAM3 model is

>>>>

This study has identified some correlations between variables within South America. However, all mention of causality has been carefully avoided, as there is not enough evidence to say that e.g. a decrease in precipitation has lead to a decrease in NPP in South America. A further line of enquiry could be to look for causal links between the variables that have been correlated together here. To do this, it is likely that the data would have to be analysed without taking temporal means, so as it could be established if the change in one particular variable preceeded the change in another (implying causation). Alternatively, the model itself could be modified so as certain aspects of the land surface scheme, MOSES, could be turned on or off, as is done currently for the radiation scheme currently \parencite{pope2000impact}.
